target_offtarget

### 2025-02-04 manuscript_figures.Rmd
Alternative plot for Fig S13

depth_both <- rbind(kobu_depth, cardio_depth)

depth_both$type <- depth_both$type %>%
  case_match("dedup_TE" ~ "dedup",
             .default = depth_both$type)

@@

depth_both |>
  filter(Background != "p6") |>
  filter(type == "dedup") |>
  filter(mapper == "bowtie2") |>
  filter(Viral.load != "NA") |>
  ggplot(aes(
    x = Viral.load,
    y = (mean_depth),
    colour = Background
  )) +
  geom_point() +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "none", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +  
  facet_grid(Background ~ virus, labeller = as_labeller(coverage_labels)) +
  scale_color_manual(values = cols2) +
  ylab("Mean read depth") +
    xlab("Spike-in viral load (gc/ml)") +

   scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))

ggsave("figures/manuscript_figure_2025/PDF/Figure_S13.pdf",
       width=8,
       height=4)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S13.png",
       width=8,
       height=4)

>>>>

cardio_depth_poly <- 
  read.table(
    "data_cardiovirus/cardiovirus_denovo_bowtie2_readdepth_per_sample_dedup_polyomics.tsv",
    sep = ",",
    header = TRUE
  ) |>
  select(-contig_name) |>
  filter(Background %in% c("S18", "S19", "S43")) |>
  select(-Background) |>
  separate(Sample_id, into = c(NA, NA, "Background"), sep = "-", remove = FALSE)

depth_both <- rbind(kobu_depth, cardio_depth, cardio_depth_poly) |>
  mutate(Viral.load = ifelse(is.na(Viral.load), 0, Viral.load))

depth_both$type <- depth_both$type |>
  case_match("dedup_TE" ~ "dedup",
             "dedup_polyomics" ~ "dedup",
             .default = depth_both$type)

depth_both$Sample_id <- depth_both$Sample_id |>
  case_match("RNA-Msp-p2" ~ "P1",
             "RNA-Msp-p8" ~ "P2",
             "RNA-Msp-p6" ~ "P3",
             .default = depth_both$Sample_id
             )

depth_both$virus <- depth_both$virus |>
  case_match("cardiovirus" ~ "Cardiovirus",
             "k97_19971" ~ "Kobuvirus",
             .default = depth_both$virus
             )

@@

depth_both$Viral.load <- factor(depth_both$Viral.load, labels = c("Shotgun",
    "10^{2}", 
    "10^{3}", 
    "10^{5}"
    ))

# depth_both |>
#   filter(Background != "p6") |>
#   filter(type == "dedup") |>
#   filter(mapper == "bowtie2") |>
#   filter(Viral.load != "NA") |>
#   ggplot(aes(
#     x = Viral.load,
#     y = (mean_depth),
#     colour = Background
#   )) +
#   geom_point() +
#  theme_few() +
#   theme(
#     axis.title.x = element_text(size = 12),
#     axis.title.y = element_text(size = 12),
#     legend.title = element_blank(),
#     legend.position = "none", 
#     panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
#     panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
#   ) +  
#   facet_grid(Background ~ virus, labeller = as_labeller(coverage_labels)) +
#   scale_color_manual(values = cols2) +
#   ylab("Mean read depth") +
#     xlab("Spike-in viral load (gc/ml)") +
#    scale_x_log10(labels = scales::trans_format("log10",
#                                         scales::label_math())) + 
#   scale_y_log10(labels = scales::trans_format("log10",
#                                         scales::label_math()))

# replotting S13 in similar way to S14
depth_both %>%
  filter(Background != "p6") |>
  filter(type == "dedup") |>
  filter(mapper == "bowtie2") |>
  # filter(Viral.load != "NA") |>
  ggplot(aes(x = Sample_id, y = mean_depth, color = Background)) +
  geom_point() +
  ylab("Mean read depth") +
  xlab("Sample ID") +
  facet_grid(virus ~ Viral.load,
             scales = "free_x",
             label = label_parsed) +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) +
 theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )+
  scale_y_log10(labels = scales::trans_format("log10",
                                        scales::label_math()))

ggsave("figures/manuscript_figure_2025/PDF/Figure_S13_v2.pdf",
       width=8,
       height=4)

ggsave("figures/manuscript_figure_2025/PNG/Figure_S13_v2.png",
       width=8,
       height=4)
